Corporate Security Solutions for BYOD:\\ A Novel User-Centric and Self-Adaptive System

### 2015-06-16 MUSES_vs_BYOD_solutions.tex
Re-writing another paragraph to avoid forward slashes, and to improve it in general. Related to #38

Moreover, it has been demonstrated that employees who ignore the company security policies are the main hazard for the company security \cite{Adams_Users05}. In this situation, the tools that are appearing in the market aim to cope with the concept of seamless working experience on different devices. This concept is a methodology of work which allows users to start/continue a working session, over multiple devices and locations, without any significant loss of data. This new situation has a big impact from the point of view of the security \cite{Schu_SecPatterns05}, since the company data borders have changed in the last years, ans therefore now the users can access important data from outside the enterprise, and possibly through a non absolutely secure channel. %Antares - Yo quitaba lo de significant loss of data, ya que significant se repite después.
%Cambiado

>>>>

Moreover, it has been demonstrated that employees who ignore company security policies are the main hazard for company security \cite{Adams_Users05}. In this situation, the tools that are appearing in the market aim to cope with the concept of seamless working experience on different devices. This concept is a methodology of work which allows users to start, or continue a working session, over multiple devices and locations, without any significant loss of data. This new situation has a big impact from the point of view of the security \cite{Schu_SecPatterns05}, since company data borders have changed in the last years. Therefore, now the users can access important data from outside the enterprise, and possibly through a non completely secure channel. %Antares - Yo quitaba lo de significant loss of data, ya que significant se repite después.
%Cambiado
